SDR enhancement by clouds

### 2024-03-21 article/article.Rmd
Commit 2024-03-21 14:14

For completeness we will describe the main points of the radiation simulation
procedure here.  We used as input the spectrum of @Kurucz1994 in the range $280$ to
$2500\,\text{nm}$.

@@

We simulated
the clear sky radiation, using the solar radiation , with a SZA step of $0.2^\circ$.
For the
atmospheric characteristics, we used combinations of AOD at $500\,\text{nm}$
($t_{500\text{nm}}$) and additional offsets of $\pm1$ and $\pm2\sigma$, water column
($w_h$) with offsets of $\pm1$ and $\pm2\sigma$, and applied it to two atmospheric
profiles "AFGL atmospheric constituent profile, midlatitude summer" (afglms) and
"AFGL atmospheric constituent profile, midlatitude winter" (afglmw) [@Anderson1986].
Thus, we were able to emulate different atmospheric condition and level of
atmospheric clearness for the climatological conditions of the site.

@@

- rte_solver  disort
- geometry   pseudospherical
- mol_abs LOWTRAN

>>>>

For completeness, we will describe here the main points of the radiation simulation
procedure. We used as input the spectrum of @Kurucz1994 in the range $280$ to
$2500\,\text{nm}$, with the radiation transfer solver "disort" on a "pseudospherical"
geometry and the "LOWTRAN" gas parameterization.

@@

We simulated
the clear sky radiation, using the solar radiation , with a SZA step of $0.2^\circ$.

For the
atmospheric characteristics, we iterated combinations of AOD at $500\,\text{nm}$
($t_{500\text{nm}}$) and additional offsets of $\pm1$ and $\pm2\sigma$, and water column
($w_h$) with offsets of $\pm1$ and $\pm2\sigma$, and applied it to two atmospheric
profiles "AFGL atmospheric constituent profile, midlatitude summer" (afglms) and
"AFGL atmospheric constituent profile, midlatitude winter" (afglmw) [@Anderson1986].

Thus, we were able to emulate different atmospheric condition and level of
atmospheric clearness for the climatological conditions of the site.

@@

### 2024-03-21 article/article.tex
Commit 2024-03-21 14:14

For completeness we will describe the main points of the radiation simulation
procedure here. We used as input the spectrum of Kurucz (1994) in the range \(280\) to
\(2500\,\text{nm}\).

@@

We simulated
the clear sky radiation, using the solar radiation , with a SZA step of \(0.2^\circ\).
For the
atmospheric characteristics, we used combinations of AOD at \(500\,\text{nm}\)
(\(t_{500\text{nm}}\)) and additional offsets of \(\pm1\) and \(\pm2\sigma\), water column
(\(w_h\)) with offsets of \(\pm1\) and \(\pm2\sigma\), and applied it to two atmospheric
profiles ``AFGL atmospheric constituent profile, midlatitude summer'' (afglms) and
``AFGL atmospheric constituent profile, midlatitude winter'' (afglmw) (Anderson et al. 1986).
Thus, we were able to emulate different atmospheric condition and level of
atmospheric clearness for the climatological conditions of the site.

@@

\begin{itemize}
\tightlist
\item
  rte\_solver disort
\item
  geometry pseudospherical
\item
  mol\_abs LOWTRAN
\end{itemize}

>>>>

For completeness, we will describe here the main points of the radiation simulation
procedure. We used as input the spectrum of Kurucz (1994) in the range \(280\) to
\(2500\,\text{nm}\), with the radiation transfer solver ``disort'' on a ``pseudospherical''
geometry and the ``LOWTRAN'' gas parameterization.

@@

We simulated
the clear sky radiation, using the solar radiation , with a SZA step of \(0.2^\circ\).

For the
atmospheric characteristics, we iterated combinations of AOD at \(500\,\text{nm}\)
(\(t_{500\text{nm}}\)) and additional offsets of \(\pm1\) and \(\pm2\sigma\), and water column
(\(w_h\)) with offsets of \(\pm1\) and \(\pm2\sigma\), and applied it to two atmospheric
profiles ``AFGL atmospheric constituent profile, midlatitude summer'' (afglms) and
``AFGL atmospheric constituent profile, midlatitude winter'' (afglmw) (Anderson et al. 1986).

Thus, we were able to emulate different atmospheric condition and level of
atmospheric clearness for the climatological conditions of the site.

@@
